Index measures for oak decline severity using phenotypic descriptors

### 2020-01-22 manuscript/manuscript.Rmd
altered LIME methods to include the defined example cases

To identify which phenotypic descriptors contributed locally to specific example cases of each of the decline indexes, Local Interpretable Model-Agnostic Explanations (LIME) were computed [@ribeiro2016].  
For the PDI, the example cases consisted of selecting three trees scores closest to 0 (healthy), 0.5 (moderate) and 1 (severely declining) respectively.
For the DAI, five example cases were selected from trees with PDI scores greater than 0.5.
These cases incuded a decline neutral case with a score closest to 0 and then for each of the AOD and COD syndromes, a moderate and a severe case were selected with scores closes to 0.5 and 1 for AOD and -0.5 and -1 for COD respectively. 
LIME analysis was conducted using the lime R package version `r packageVersion('lime') %>% as.character()` with the default parameters [@pedersen2019].

>>>>

To identify which phenotypic descriptors contributed locally to specific example cases of each of the decline indexes, Local Interpretable Model-Agnostic Explanations (LIME) were computed [@ribeiro2016]. 
The example cases included the trees with the minimum (0) and maximum (1) PDI values and the tree with the PDI value closest to the median for the healthy, severe and moderately declining trees respectively.
For the DAI, five example cases were selected from trees with PDI scores greater than 0.5.
These cases incuded a decline neutral case with a score closest to 0 and then for each of the AOD and COD syndromes, a moderate and a severe case were selected with scores closes to 0.5 and 1 for AOD and -0.5 and -1 for COD respectively. 
LIME analysis was conducted using the lime R package version `r packageVersion('lime') %>% as.character()` with the default parameters [@pedersen2019].
